---
title: "main"
author: "Benjamin"
date: '2019-04-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Dependencies

```{r}
keyring, glue
```


```{r}
devtools::document()
devtools::load_all()
devtools::install()

```

MAILTO="bguinaudeau@gmail.com"
1 2 3 4 5 /root/backup.sh >/dev/null 2>&1

1: Minute (0-59)
2: Hours (0-23)
3: Day (0-31)
4: Month (0-12 [12 == December])
5: Day of the week(0-7 [7 or 0 == sunday])
/path/to/command – Script or command name to schedule


Special string	Meaning
@reboot	Run once, at startup.
@yearly	Run once a year, “0 0 1 1 *”.
@annually	(same as @yearly)
@monthly	Run once a month, “0 0 1 * *”.
@weekly	Run once a week, “0 0 * * 0”.
@daily	Run once a day, “0 0 * * *”.
@midnight	(same as @daily)
@hourly	Run once an hour, “0 * * * *”.

```{r}

exec <- function(string, cmd = F, ...) if(cmd == T) return(string) else return(system(string, ...))
append <- function(path, string, cmd = F) exec(glue::glue("echo { string } >> { path }"), cmd = cmd)
source_cli <- function(path, cmd = F) exec(glue::glue("Rscript { path }"), cmd = cmd)
current_user <- function() system("echo $USER", intern = T)

source_cli("~/Downloads/a.R", cmd = T)

append("~/Downloads/crontab", "1")
script_path <- "~/Downloads/a.R"
crontab_path <- "~/Downloads/crontab"

add_crontab <- function(
  user = current_user(),
  script_path = NULL,
  crontab_path = NULL,
  meta = NULL,
  min = "0-59/2", 
  hour = "*",
  date_day = "*",
  date_month = "*",
  day = "*", 
  cmd = F,
){
  
  command <- source_cli(script_path, cmd = T)
  
  if(!is.null(meta)){
    time_pattern <- meta
  } else {
    time_pattern <- paste(min, hour, date_day, date_month, day)
  }
  
  append(
    crontab_path,
    glue::glue("{ time_pattern } { user } { command }")
  )
}

```

